


>>>>>>> Stashed changes
# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

1. There are the following 16 variables: Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres
, TotalLivingArea, Bedrooms, FinishedBsmtArea (sf), LotArea(sf), AC, FirePlace, and Neighborhood. After running "?ames" we were able to
get a description of each variable. We are anticipating that numerically price will be in the thousands, or hundreds of thousands,
addresses within Ames zipcodes (shouldn't be too many options), year can range from the first house built in ames (~200 years prior)
until 2024, bedrooms will be a single digit value, some are boolean variables (fireplace, finished basement, ac), lot area will be
measured in acres and will be in the hundreds or more. 
```{r}
library(classdata)
data(ames)

?(ames)
```

2. The variable of interest for our group is "Price". 

3. The histogram below shows that there most of the houses in Ames are within a relatively similar price range. However, there are a few outliers, two of which are above the 10 million dollar mark.
```{r}

```

4. We did not notice we that the variable of focus for the next slide was going to be "Sale Price" as we focused on that for the slide before. So, our steps 1-3 would be repetitive, but we did include an extra variable to compare it with.

```{r}
library(ggplot2)

ames$`Sale Price` <- as.numeric(as.character(ames$`Sale Price`))

ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(binwidth = 100000, fill = "skyblue", color = "black") +
  labs(title = "Histogram of Sale Prices", x = "Sale Price", y = "Frequency") +
  theme_minimal()
```

```{r}
# Range for `Year Built`
ggplot(ames, aes(x = `YearBuilt`)) +
  geom_histogram(binwidth = 10, fill = "blue", alpha = 0.3, color = "black") + 
  scale_x_continuous(name = "Year Built") +
  theme_minimal() +
  xlim(1850, 2024)
# The range for Year Built is between 1880 and 2022, with some homes having an NA value.
# This histogram is skewed left, meaning more homes were built recently.

# Relationship to main variable
ggplot(ames,
       aes(x = YearBuilt,
           y = `Sale Price`
           )) +
  geom_point(color = "blue", alpha = 0.3) +
  xlim(1850, 2024)

# From the looks of it, regardless of the year the house was built, the sale price
# seems to be about the same, so there isn't much of a relationship between year built and
# sale price. There are about 5-6 outliers whose prices are much higher than the other      
# homes. These outliers were all built around the year 2000 or after.
```

```{r}
# Range for `Acre`
ggplot(ames, aes(x = Acres)) +
  geom_histogram(binwidth = 1, fill = "blue", alpha = 0.3, color = "black") + 
  scale_x_continuous(name = "Acres") +
  theme_minimal() +
  xlim(0, 20) +
  ylim(0, 25)
# The range for Acres is between 2.5 and 12.5. It is right skewed as there is an outlier within the 12.5 area.

# Relationship to main variable
ggplot(ames,
       aes(x = Acres,
           y = `Sale Price`,
           color = "blue", alpha = 0.3)) +
  geom_point() +
  xlim(0, 20)

# A majority of the points are in the bottom left corner, meaning they're all about the same price when the acrage is 5 or less. There are two dots at the top, both outliers, whose prices are much higher than the majority even though the acrage is less than 5. There are also two dots past 5 acres, also outliers, but their price is about the same as the majority of the houses. There isn't too much of a relationship between Acres and Sale Price due to the cluster in the bottom left corner. 
```

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(classdata)
data("ames")
?ames
head(ames)
```

<<<<<<< Updated upstream
```{r setup, include=FALSE}
library(classdata)
data("ames")
?ames
```
=======
```{r}
ggplot(data = ames, aes(x = `Sale Price`)) +
  geom_histogram(binwidth = 100000, color = "black") +
  labs(title = "Histogram of Sale Price",
       x = "Sale Price",
       y = "Frequency")

ggplot(data = ames, aes(x = `Sale Price`, y = `LotArea(sf)`)) +
  geom_point(color = "blue", size = 3, alpha = 0.8) +  # Customize point appearance
  scale_x_log10() +  # Use log scale for x-axis (Sale Price)
  scale_y_continuous(labels = scales::comma, breaks = scales::pretty_breaks()) +  # Format y-axis labels
  theme_minimal() +  # Minimal theme
  labs(x = "Sale Price", y = "Lot Area", title = "Scatter Plot of Sale Price vs Lot Area")  # Axis labels and title

#Most of the dots are in the bottom left, this signifies that houses with smaller lot area, are generally 
#cheaper. There are a few outliers though around the bottom right side, meaning that their price is high,
#but they still dont have a lot of lot area.
```
```{r}
#Range for occupancy 
ggplot(ames, aes(x = `Occupancy`)) +
  geom_histogram(binwidth = 1, stat = "count")

#Linear plot
ggplot(ames, aes(x = Occupancy, y = `Sale Price`)) +
  geom_point() +
  labs(x = "Occupancy", y = "Sale Price") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal()

#Log plot

ggplot(ames, aes(x = Occupancy, y = `Sale Price`)) +
  geom_point() +
  labs(x = "Occupancy", y = "Sale Price (log scale)") +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal() +
  scale_y_continuous(trans = "log10") 
#Log scale for y variable makes data much clearer (compared to linear)

```
The range for Occupancy is Condominium, Single Family, Townhouse, Two-Family, Two-Family Duplex, and NA
I assumed that sale price would have a correlation with these variables as they have an impact on size and 
living style of each home. There were significantly more Single Family/Owner Occupied homes (~ 4700) 
than any other type of homes in Ames, the next most common being condominiums and Townhomes (~700 each). 
When formatting a scatterplot, using a linear pattern for sale price showed that there were similar 
pricings for different types of homes with two extreme outliers for Condominiums that had a much higher 
sale price comparitively. After changing sale price to a log scale, the ranges of sale price was much more
evident. The same two outliers with extremely high sale prices are obvious on this scatterplot too, with 
some added lower scale outliers for almost every type of home. The largest range of sale price being NA 
(to be expected), lowest range being Two-Family Duplex, the highest prices being Condominiums, and lowest 
is sort of unclear with the scatterplot. These are all important relationship characteristic connecting 
Occupancy type to sale price. 


