---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

1. There are the following 16 variables: Parcel ID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres
, TotalLivingArea, Bedrooms, FinishedBsmtArea (sf), LotArea(sf), AC, FirePlace, and Neighborhood. After running "?ames" we were able to
get a description of each variable. We are anticipating that numerically price will be in the thousands, or hundreds of thousands,
addresses within Ames zipcodes (shouldn't be too many options), year can range from the first house built in ames (~200 years prior)
until 2024, bedrooms will be a single digit value, some are boolean variables (fireplace, finished basement, ac), lot area will be
measured in acres and will be in the hundreds or more. 

2. The variable of interest for our group is "Price". 

3. 


```{r}
library(classdata)
data(Ames)
?(ames)
